---
title: "NaRnEA - User Guide Part 1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NaRnEA - User Guide Part 1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

Non-parametric analytical Rank-based Enrichment Analysis (NaRnEA) is a novel statistical method created by [Griffin et al.](https://www.biorxiv.org/search/NaRnEA) for the purpose of performing powerful and accurate gene set analysis. 

## Installing NaRnEA

The NaRnEA R package can be installed from the [Califano Lab Github](https://github.com/califano-lab/NaRnEA) using the `devtools` R package with the following code.
```{r, eval = FALSE}
devtools::install_github(repo = "califano-lab/NaRnEA", force = TRUE, build_vignettes = TRUE)
```

## Simulated Gene Set Analysis with NaRnEA

We can first evaluate NaRnEA's capacity for performing powerful and accurate gene set analysis using some simulated data.

```{r, eval = FALSE}
sim.seed <- 11

gene.num <- 20000

null.ges.min <- -10
null.ges.max <- 10

gene.set.size <- 100

alt.ges.min <- 5
alt.ges.max <- 10
```

## Inferring Master Regulators of Lung Adenocarcinoma with NaRnEA

Information




